\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={5in, 9in}]{geometry}
\title{Retrospective}
\begin{document}
\date{}
\maketitle
\pagenumbering{arabic}
\section*{What went well?}
\begin{itemize}
\item The communication in the group has been a lot better since the last iteration.
\item One of the things we agreed to work with in this iteration was organizing the tasks, so in this iteration we started with going through all the tasks, and dividing all the big tasks into smaller ones.
\item We've been more time effective this time.
\item We've spent some time refactoring the code, so would be easier to read and develop further. This made the current iteration easier to complete, since we could more effectively make changes to the code.
\item We started with stand-up meeting to improve our Scrum process, which worked very well. The meetings became a lot shorter and more effective. Everybody quickly informed the rest of the group what they have been doing and what they are going to do next. 
\end{itemize}
\section*{What could have gone better?}
\begin{itemize}
\item We're still not using Git issues to it's full potential. We need to get better at moving the tasks from "to do" to "doing" and then close them.
\item We want to become even better with communication, so we've made a new house rule, which states that if you can't come to a meeting, you are obligated to inform the rest of the group and let them know what you have been working on and what you will continue to work on.
\end{itemize}
\end{document}


- Ryddet i koden, enklere å forstå
- Ganske greit å gjøre endringen i denne iterasjonen, koden var lett å endre og fungerte bra
- Stand up møtene var korte og effektive, bra i forhold til scrum
- Tatt ordentlig tak i det som ikke var bra sist og jobbet godt med det
- Issue boardet er ikke helt up to date, må bli flinkere til å flytte oppgavene til Doing, Done osv
- Kan bli enda bedre på kommunikasjon
- Ny regel: Hvis du ikke kan komme på en møte, informer gruppen og skriv hva du holder på / har gjort.