\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={5in, 9in}]{geometry}
\title{Retrospective}
\begin{document}

\date{}
\maketitle
\pagenumbering{arabic}
\section*{What went well?}
\begin{itemize}
\item Git has worked well. There has not been many issues with merging, or other issues.
\item The result so far is very good.
\item The logic that we made for classes in Oblig 2 has worked very well. It has been easy to work with, and caused minimal problems when implementing.
\item We are very happy about our choice with LibGDX, it has been relatively easy to work with.
\item Everybody is very happy to have a new group member!
\item TDD went better than we thought it would.
\end{itemize}

\section*{What could have gone better?}
\begin{itemize}
\item There has been some unstable attendance in the group, and sometimes a bit difficult to get in touch with people. We need to become better at informing the group if we are not able to attend a group meeting, and for what reason.
\item Communication in the group this time has not been the best.
\begin{itemize}
\item We could be more organized in making the tasks, so that it is easier for everyone to know what they are supposed to do. We have not used Git issues optimally.
\item We have encountered some difficulties regarding assigning tasks to group members, and ended up with people doing the same tasks. We must work on making it easier and more clear to which task is assigned to whom.
\end{itemize}
\item The code is not as clean as desired, and Java Doc has not been written for every method when it should have been written
\item We did not manage the time we had well enough and ended up in a time clamp.
\item Even though TDD went better than expected, we did not write enough tests and found that it was a bit challenging.
\item We agreed on using Scrum, but we could have done a better job organizing meetings and going through what has been done and what was left to do.
\end{itemize}
\end{document}