\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={5in, 9in}]{geometry}
\title{Retrospective}

\begin{document}
\date{}
\maketitle
\pagenumbering{arabic}
\section*{What went well?}
\begin{itemize}
\item In this iteration, we decided that we wanted to assign bigger task to a group of people, instead of dividing all the tasks into smaller tasks and then dividing them. For example on group got tasked with the feature multi player online, and another group would finish the AI for the intermediate and hard levels. This worked very well, since everybody got a clear picture of the assigned task and there was a person in charge of every task.

\item Amund added a confetti animation in the game, which made the application even more fun for kids!

\item The communication continues to improve. More people are responding on Slack and the communications is smoother.

\item The meetings we've had in this iteration have been very efficient. We're very pleased with the stand-up meetings, which gives everyone a overview of how much we've accomplished and what's left to do.

\item Since there was several new features to be implemented, we decided that every feature should have its own branch. This made the implementation a lot easier to do, since we could always test our own code, without expecting bugs from the other features.
\end{itemize}
\section*{What could have gone better?}
\begin{itemize}
\item The attendance at meetings have been somewhat unstable because not everyone met on point.
\item Our Scrum process is still not as good as it could be. For example, we could have divided the larger tasks into smaller ones, so that we could track the process a bit better.
\end{itemize}
\section*{New activities / tools}
\begin{itemize}
\item If we were to make another application with online playing, we would like to do this with sockets instead.
\item In the new programming project we will focus more on test driven development (TDD).
\item We would like use the Model-View-Controller software pattern, to make it easier to reuse code and to keep the components separate.
\end{itemize}
\end{document}
