\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Retrospective}

\begin{document}
\maketitle

\section{What went well?}

\begin{itemize}
\item We found that breaking bigger tasks into smaller pieces to be solved separately, was an effective way of working. We were also satisfied with the amount of work everyone was assigned.
\item We found that the workload and the amount of time we allotted agreed well.
\item Good communication between the team members and conflictless meetings.  
\item Everyone has been present at every meeting. 
\end{itemize}

\section{What could have gone better?}
\begin{itemize}
\item We could advantageously have been more prepared for each meeting by reading through the tasks and lecture notes on beforehand.  
\item  The conversation has had a tendency to sometimes turn towards subjects that don't have to do with the project. The tasks haven't been too demanding and we have had some leftover time, so we expect that a more detailed plan on what is to be done during each meeting and a tighter time scheme will solve this issue.
\end{itemize}

\section{What do we want to try?}
\begin{itemize}
\item GitLab
\item Scrum 
\item libGDX
\end{itemize}


\end{document}