\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

%opening
\title{Fully Dressed User Cases}
\author{}
\usepackage{scrextend}

\usepackage{hyperref}


\begin{document}

\maketitle

\section*{Use Case UC1: Game against a player}

\textbf{Scope:} Chess application
\\\\
\textbf{Level:} User goal
\\\\
\textbf{Primary Actor:} \texorpdfstring{Player\textsubscript{1}}{Player 1}
\\\\
\textbf{Stakeholders and Interests:} 
\begin{itemize}
 \item \textbf{\texorpdfstring{Player\textsubscript{1}}{Player 1} and \texorpdfstring{Player\textsubscript{2}}{Player 2}:} Wants easy to understand and use, responsive game. Wants to only be able to do valid chess moves. Wants fair ranking system. Wants to be able to play against a AI with chosen difficulty.
 \item \textbf{Developers:} Wants the users to not crash the application.
\end{itemize}
\textbf{Preconditions:} Both players are registered
\\\\
\textbf{Success Guarantee:} Players are able to start a game of chess against each other. 
\\\\
\textbf{Main Success Scenario:}
\begin{enumerate}
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} starts application.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} logs in.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} enters the start screen.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} chooses to play against a human player.
 \item \texorpdfstring{Player\textsubscript{2}}{Player 2} logs in.
 \item Randomly \texorpdfstring{Player\textsubscript{2}}{Player 2} and \texorpdfstring{Player\textsubscript{2}}{Player 2} are given either white or black pieces.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} and \texorpdfstring{Player\textsubscript{2}}{Player 2} starts a game of chess
 \end{enumerate}
\textbf{Extensions:}
\begin{addmargin}[1.4em]{0em}

2a. \texorpdfstring{Player\textsubscript{1}}{Player 1} does not have a user.
\begin{enumerate}
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} selects the register button.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} enters details.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} logs in.
\end{enumerate}
3a. \texorpdfstring{Player\textsubscript{1}}{Player 1} chooses to play against a CPU.
\begin{enumerate}
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} chooses between difficulties beginner, intermediate or expert.
 \item Randomly \texorpdfstring{Player\textsubscript{1}}{Player 1} and the CPU are given either white or black pieces.
 \item \texorpdfstring{Player\textsubscript{1}}{Player 1} and the CPU starts a game of chess.
\end{enumerate}
4a.  \texorpdfstring{Player\textsubscript{2}}{Player 2} does not have a user.
\begin{enumerate}
 \item \texorpdfstring{Player\textsubscript{2}}{Player 2} selects the register button.
 \item \texorpdfstring{Player\textsubscript{2}}{Player 2} enters details.
 \item \texorpdfstring{Player\textsubscript{2}}{Player 2} logs in.
\end{enumerate}
\end{addmargin}
\section*{Case UC2: User wants to show his/her ranking.}

\textbf{Scope:} Chess application.
\\\\
\textbf{Level:} User goal.
\\\\
\textbf{Primary Actor:} Player.
\\\\
\textbf{Stakeholders and Interests:}
\begin{itemize}
 \item \textbf{Player:} Want easy to use menus, wants to understand the statistics and it contains at least some of the statistics the user wants. 
 \item \textbf{Developers:} Wants the users to not crash the application.
\end{itemize}
\textbf{Preconditions:} The player is registered
\\\\
\textbf{Success Guarantee:} The player is able to check his/her score.
\\\\
\textbf{Main Success Scenario:}
\begin{enumerate}
 \item Player starts application.
 \item Player logs in.
 \item Player enters the start screen.
 \item Player clicks "Show Statistics".
 \item Player clicks "Show Ranking".
\end{enumerate}
\textbf{Extensions:}
\begin{addmargin}[1.4em]{0em}
2a. Player does not have a user.
\begin{enumerate}
 \item Player selects the register button.
 \item Player enters details.
 \item Player logs in.
\end{enumerate}
\end{addmargin}
\end{document}
