\documentclass{article}

\title{User Stories}

\begin{document}

\date{}
\maketitle

\begin{enumerate}

\item	As a player I want the other person to lose if they quit before the game ends, so it is fair.

\item	As a family we should be able to easily switch between users, so that we don’t have to share a rank.

\item	As a user I want to be able to choose between playing against the computer, and another person, so that I can play alone, or with others.

\item	As a user I want to be able to change the difficulty of the computer so that it fits most skill levels. 
		(Novice, Intermediate, Advanced)

\item	As a child I want to be able to see the rules of the game, so that I can learn easily.

\item	As a user I want to be able to choose which color I have, so that I can practice both sides. 

\item	As a child I want an easy to use interface, so that I can understand it.

\item	As a busy person I should be able to ask for a draw, so that I can stop playing at any time, and not waste time.

\item	As a player I want the game to show me when a move is invalid or valid, so that I get some visual feedback.

\item	As a user I want an option to see a history of my games played.

\item	As a user I should be able to set a time limit to turns, so that I can control the game's intensity. 

\item	As a user I want the game to show me when a king is in check, so I can make an appropriate move.

\item	As a user I want to see which pieces are taken, so that I can have an overview of the game.

\item	As a user I want the game to show me the last move made, in case I miss it.

\item 	As a user I want to see all valid moves when i click a chess piece, so that I can easily see what's available.   

\item 	As a chess player I want to be able to do advanced moves, like castling or "en passant", so that the game mirrors real life chess.

\item	As a chess player I want all special rules for draw to apply, so we don't have to waste time. 

\item	As a competitive teenager I want to be able to create a personal user, so I can be part of a ranking system.

\item	As a competitive teenager I want to be able to see my ranking, so that I can compare myself to other players.

\item	As a player I want to be able to exchange my pawn with my choice of queen, rook, bishop, or knight, if i move it to the opponent's side. 

\item	As a user I should be able to see who's turn it is, so that I know if I need to pay attention.

\item	As a user i want the game to end, showing me who won, when a game ending criteria is met, so that i know who won.

\item	As a player I want the end game screen to show me my new ranking, so that I get an update on how I'm doing.

\end{enumerate}

\end{document}
