\documentclass[norsk]{article}

\title{Process- and Projectplan}
\begin{document}
	\maketitle
\section{Process}
We decided to use Scrum as our framework for our project process. We will have our Scrum meetings every monday. At these meetings we will discuss what tasks we finished in the sprint, and delegate new tasks for the next sprint. Our sprint's will extend over one week. 

We choose Scrum because everybody will be present and involved when we distrubute tasks for the sprint. This will help us to hand out tasks such that no one will work on the same tasks, and make sure that no tasks are left behind. Handing out spesific tasks with a deadline will also make it easier for the groupmembers to estimate how much time they have to set aside for the sprint. 

We will use Gitlab to handle our backlog, by making issues, and than working on them during the sprint. 
 
 \section{Organizing}
 We will meet every monday, from 14.00 to 17.00. This meeting will mainly focus on handing out new tasks and evaluating finished tasks. But we will also work together on the task at the monday meeting, and we will be able to discuss and ask each other for help.
  Outside of the monday-meetings our comunication will be handled in slack. 
  We will use gitlab to store our common files. The repository will consist of two branches, master and develop. We will merge the develop branch into master once a week. The idea is to always have a working program in the master-branch.
  
  In an attempt to avoid conflict and proplems during the project, we will try to:
  
  \begin{itemize}
  	\item 
  	Share knowledge, such that there is always more than one person that knows how something works in case that one person is sick or quits.
  	\item 
  	Be clear on who is responsible for a task.
  	\item 
  	Set and respect deadlines.
  	\item 
  	Write readable code. We will discuss and choose a style-guide when we start writing code. 
  	\item 
  	Be open to constructive criticism.
  	\item
  	If a confict occurs, first deal with the persons involved. 
 \end{itemize}
	
\end{document}